---
title: "My Title"
author: "My name"
date: today
---

## Code longevity of the R programming language

Using R 4.2.2 on Ubuntu 22.04, I ran every example contained in the man/ folder of every default R
packages that get installed alongside R. The list of these packages contains the well-known 
`{base}` and `{stats}` packages among others.

The graph and table below shows the result; regardless of version, most of the time

```{r}
tar_read(errors_plot)
tar_read(errors_table)
```

Some slight modification had to be made to make certain examples run. The table below shows 
which modifications where made for which packages. All the modifications consisted in loading
`{stats}` or `{stats4}` instead of the original packages (like `{modreg}`). This is because
these packages don't exist in current versions of R, but the functions do; so because these
functions were moved to another package, the correct, current package had to be loaded for these
examples to run. The table below shows which packages and which versions of R where impacted.

```{r}
tar_read(fix_table)
```

...
.
